---
title: "p8105"
author: "Qing Xu"
date: "November 21, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(haven)
library(readxl)
library(janitor)
library(ggmap)
library(plotly)
library(stringr)
library(wordcloud2)
library(tidytext)
library(forcats)
library(viridis)
library(ggplot2)
```
#clean data
```{r}
nyc_jobs<- read.csv("NYC_Jobs.csv") %>%
  clean_names() %>%
  filter(job_category!= " ", 
         full_time_part_time_indicator!=" ", 
         preferred_skills!= " ",
         work_location!=" ") %>%
  head(2500) #google map limited to 2500
nyc_jobs$job_category<- as.character(nyc_jobs$job_category)

#combine job category (function?)
for (i in 1:2500) {
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("engineering", ignore_case = TRUE))] <- "Engineering"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("finance", ignore_case = TRUE))] <- "Finance"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("legal", ignore_case = TRUE))] <- "Legal Affairs"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("technology", ignore_case = TRUE))] <- "Technology"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("policy", ignore_case = TRUE))] <- "Policy"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("communi", ignore_case = TRUE))] <- "Community"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("clerical", ignore_case = TRUE))] <- "Clerical"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("social service", ignore_case = TRUE))] <- "Social service"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("public safety", ignore_case = TRUE))] <- "Public safety"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("administration", ignore_case = TRUE))] <- "Administration"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("operations", ignore_case = TRUE))] <- "Maintance"
    nyc_jobs$job_category[[i]][str_detect(nyc_jobs$job_category[[i]],regex("maintenance ", ignore_case = TRUE))] <- "Maintance"
    
}


# change unit of salary and calculate mean
nyc_jobs$salary_frequency<-as.character((nyc_jobs$salary_frequency))
nyc_jobs$salary_range_from<- as.numeric(nyc_jobs$salary_range_from)
nyc_jobs$salary_range_to<- as.numeric(nyc_jobs$salary_range_to)

#function?
nyc_jobs$salary_range_from <- with(nyc_jobs, ifelse(salary_frequency == "Hourly", salary_range_from*1825,salary_range_from))
nyc_jobs$salary_range_to <- with(nyc_jobs, ifelse(salary_frequency == "Hourly", salary_range_to*1825,salary_range_to))
nyc_jobs$salary_range_from <- with(nyc_jobs, ifelse(salary_frequency == "Daily", salary_range_from*365*5/7,salary_range_from))
nyc_jobs$salary_range_to <- with(nyc_jobs, ifelse(salary_frequency == "Daily", salary_range_to*365*5/7,salary_range_to))

nyc_jobs<-mutate(nyc_jobs,salary_frequency="Annual") %>%
          mutate(salary_mean = (salary_range_to-salary_range_from)/2+salary_range_from)


# get lon and lat
nyc_jobs$work_location<-as.character(nyc_jobs$work_location)
geo <- geocode(location = nyc_jobs$work_location, output="latlon", source="google")
nyc_jobs<- nyc_jobs %>%
  mutate(lon = geo$lon, lat = geo$lat) %>%
  group_by(job_category)

```


```{r}
# plotly worldwild
Sys.setenv('MAPBOX_TOKEN' = 'pk.eyJ1IjoieHVxaW5nc2FsbHkiLCJhIjoiY2phZWh0djdyMHUzZTJ3bGR3MHFsdmIzZSJ9.vhYtu7zeAAuX6slhdDj6lA')

p <- nyc_jobs %>%
  mutate(text_label = str_c("Annual mean salary$:",salary_mean)) %>% 
  plot_mapbox(lat = ~lat, lon = ~lon,
              size=2,
              split = nyc_jobs$job_category,
              mode = 'scattermapbox') %>%
  add_markers(
    text = ~text_label,
    color = ~job_category,size = I(9)) %>%
  layout(title = 'Work Location',
         font = list(color='white'),
         plot_bgcolor = '#191A1A', paper_bgcolor = '#191A1A',
         mapbox = list(style = 'dark'),
         legend = list(orientation = 'h',
                       font = list(size = 8)),
         margin = list(l = 25, r = 25,
                       b = 25, t = 25,
                       pad = 2))
p
```

```{r} 
#alternative map
#For location in NYC(2500-611)
myLocation_nyc = c(-74.23,40.58,-73.75,40.87)
myMap_nyc <- get_map(location=myLocation_nyc,
                 source = "stamen",maptype = "watercolor", crop = FALSE) 
ggmap(myMap_nyc)+
    geom_point(aes(x = lon, y = lat), data = nyc_jobs,
      alpha = .5, color="darkred",size = 3) +
    labs(title = "Work location in NYC")

```

# Boxplot of salary in different job category
```{r}
nyc_jobs %>%
plot_ly(y = ~salary_mean, color = ~job_category, type = "box",
          colors = "Set2") %>%
layout(title = "Annual average salary distribution in 12 job categories")
```

# Job category with different educational requirement and base salary
```{r echo=False}
job_data=nyc_jobs %>%
select(job_category, salary_range_from, salary_range_to,minimum_qual_requirements,full_time_part_time_indicator,salary_frequency) %>%
filter(job_category!= " ", minimum_qual_requirements!=" ",full_time_part_time_indicator=="F",salary_frequency=="Annual")
 

x=c("baccalaureate", "Bachelor")
y=c("Master","master")

master_data=filter(job_data,grepl(paste(y, collapse = "|"),minimum_qual_requirements),!grepl(paste(x, collapse = "|"),minimum_qual_requirements))
  

baccalaureate_data = filter(job_data,grepl(paste(x, collapse = "|"),minimum_qual_requirements),!grepl(paste(y, collapse = "|"),minimum_qual_requirements))

Other_data=filter(job_data,!grepl(paste(y, collapse = "|"),minimum_qual_requirements),!grepl(paste(x, collapse = "|"),minimum_qual_requirements))
```
Boxplots of salary for different educational requirements.
```{r echo=False}
master_plot = plot_ly(master_data, y = ~salary_range_from, color = ~job_category, type = "box", colors = "Set2") %>%
layout(title = "Base salary of  jobs required at least master degree")

baccalaureate_plot = plot_ly(baccalaureate_data, y = ~salary_range_from, color = ~job_category, type = "box", colors = "Set2") %>%
  layout(title = "Base salary of jobs required at least baccalaureate degree(No need of master's)")
  
Other_plot = plot_ly(Other_data, y = ~salary_range_from, color = ~job_category, type = "box",
          colors = "Set2") %>%
  layout(title = "Base salary of different kind of jobs without requirement of degree")

```

For those three plots, we see that in the boxplot of base salary of jobs required for at least master degree, engineering has the highest median base salary and the overall base salary of Legal Affairs are pretty high compared with other job category. While in the boxplot of base salary of jobs required for baccalaureate technology has the highest median base salary, and the overall salary of Administration is pretty high compared with others. In the boxplot of base salary without requirement of degree, the median base salary and the overall base salary of Engineering are all pretty high compared with other job categories.

Comparing those three plots, we can see the overall base salary of jobs required for at least master degree are higher than the overall base salary of jobs required for baccalaureate. The distribution of the base salary of jobs without degrees' requirement is not centralized and the base salaries mainly depend on the job positon in this case.


#The wage increasing ranges of different jobs
```{r echo=False}
job_data=mutate(job_data, salary_range = salary_range_to-salary_range_from)

plot_ly(job_data, y=~salary_range, x= ~job_category, type = "bar") %>%
  layout(title = "The wage increasing ranges of different kinds of jobs")
```

From the plot, we can see that the job category of Legal Affairs has the largest wage increasing range and the job category of Clerical has the smallest wage increasing range compared with other different job categories.

## Table of positions, agency and job category. 

```{r}
job_positions = nyc_jobs %>%
  select(x_of_positions, agency, job_category, salary_mean) %>%
  distinct() %>%
  group_by(agency, job_category) %>%
  summarise(positions = sum(x_of_positions)) %>%
  arrange(desc(positions))

# Number of job positions: top 10
knitr::kable(head(job_positions, 10))
```

The table above shows the top-10 number of job positions in NYC from 2011 to 2017. `r job_positions[[1]][1]` with job category "Health" has the most job positions.

## Bar plot of job category vs. number of positions of each year.

```{r}
positions_plot = nyc_jobs %>%
  select(x_of_positions, agency, job_category, salary_mean, posting_date) %>%
  distinct() %>%
  separate(posting_date, into = c("year", "month", "day"), sep = "-") %>%
  select(-month, -day) %>%
  group_by(job_category, year) %>%
  summarise(positions = sum(x_of_positions))

plot_ly(positions_plot, x = ~job_category, y = ~positions,
        color = ~year, type = "bar") %>%
  layout(title = "Number of positions of job categories in each year",
         barmode = "group")
```

The bar chart above shows the number of positions for each job category in each year. From 2013 to 2017, the number of job positions in each category keeps increasing. And all categories have a dramatically increase in job positions in 2017. This might because more and more companies were founded and developed in 2017, thus they need more employees joining in. Besides, since this dataset contains all job information from NYC official job website, as the year increases, more people found this website and created job postings on this site.



#wordcount
```{r}
nyc_jobs = nyc_jobs%>% 
  ungroup()%>%
  mutate(  minimum_qual_requirements = as.character(minimum_qual_requirements))%>%
  mutate(preferred_skills = as.character(preferred_skills))
 
jobs_words_skill =  nyc_jobs%>%
  unnest_tokens(word,preferred_skills)%>%
  anti_join(stop_words)%>%
  inner_join(., parts_of_speech) %>%
  count(word, sort = TRUE)
jobs_words_requirement =  nyc_jobs%>%
    unnest_tokens(word,minimum_qual_requirements)%>%
    anti_join(stop_words)%>%
    inner_join(., parts_of_speech) %>%
    count(word, sort = TRUE)
  
jobs_words_skill %>% 
   top_n(20) %>% 
   mutate(word = fct_reorder(word, n)) %>% 
   plot_ly(y = ~word, x = ~n, color = ~word, type = "bar")
  
jobs_words_requirement %>% 
    top_n(20) %>% 
    mutate(word = fct_reorder(word, n)) %>% 
    plot_ly(y = ~word, x = ~n, color = ~word, type = "bar")
  
set.seed(123)
wordcloud2(jobs_words_skill, size = 2,color = 'random-light',  
           backgroundColor = "gray", fontWeight='bold',  
           minRotation = -pi/3, maxRotation = pi/3,rotateRatio = 0.8)  
wordcloud2(jobs_words_requirement, size = 2,color = 'random-light',  
           backgroundColor = "gray", fontWeight='bold',  
           minRotation = -pi/3, maxRotation = pi/3,rotateRatio = 0.8)  
```

